---
title: "R Notebook"
---

Analyzing the top different top 5 percentages in the original setup with
homophily of majorities and minorities of 0.8 towards ingroup and 0.2 towards the 
outgroup. We introduce either a share of majority as allies (majority members
who are treated as the majority by others, but prefer the minority group at the
expense of the majority group); or "invisible" minorities (minority members who
are treated as the majority by the majority and minority groups, but they
act as minority groups themselves).


Three scenarios!


First, load some packages:
```{r message = F, warning = F}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)

```


## Scenario 1 - as before

Read in the files:
```{r message = F, warning = F}
sweep_allies_1 <- read_csv("../..//python/group_A/results dpah4/allies_sweep_per_top_k_setup1.csv")
sweep_allies_1$prop_ally <- round(sweep_allies_1$prop_ally, 2)

sweep_allies_1$prop_ally_min <- sweep_allies_1$prop_ally + sweep_allies_1$prop_min
sweep_allies_1$ally_to_min <- sweep_allies_1$prop_ally / sweep_allies_1$prop_min

sweep_covert_1 <-  read_csv("../..//python/group_A/results dpah4/covert_sweep_per_top_k_setup1.csv")
sweep_covert_1$prop_covert <- round(sweep_covert_1$prop_covert, 2)
```

Plot the share of minorities across different minority share setups, with
the share of minority in top 5% of the nodes:
```{r warning = F, message=F, fig.width=16, fig.height=3.5}

# data for vertical lines - find proportion of allies for which minorities reach equity
vertical_lines_1_1 <- sweep_allies_1 %>%
  filter(beta == 0.05)%>%
  dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
  summarise(prop_min_avg = round(mean(prop_min), 2),
            prop_ally_avg = round(mean(prop_ally), 2),
            prop_min_top_k_avg = round(mean(prop_min_top_k), 2))%>%
  as.data.frame()
  
vertical_lines_1 <- vertical_lines_1[, 5:7]

vertical_lines_1 <- vertical_lines_1 %>%
  group_by(prop_min_avg)%>%
  filter(prop_min_top_k_avg >= (prop_min_avg - 0.01))%>%
  slice(which.min(prop_ally_avg))
  
data_lines_1 <- data.frame(prop_min = unique(sweep_allies_1$prop_min),  # Create data for lines
                         hline = unique(sweep_allies_1$prop_min),
                         vline = vertical_lines_1$prop_ally_avg)%>%
  filter(., prop_min < 0.5)

# plot
(plot_k_allies_1 <- sweep_allies_1 %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion))+
    facet_wrap(~ prop_min, ncol = 7)+
    geom_hline(data = data_lines_1,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_1,
               aes(xintercept = vline),
               linetype="dashed")+
        geom_text(data = data_lines_1, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
            hjust = -0.1, vjust = 1.5) +
    labs(
      title = "Effect of the increase in % of allies on the % of minorities/allies in top k  - by varying minority proportion",
      y = "% of minorities in top-k%",
      x = "Proportion allies",
      color = "Proportion of:") +
    theme_bw())
  
```

Proportion allies to minorities, a few interesting examples:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}
interesting_cases <- c(0.1, 0.2, 0.3)


sweep_allies_1_interesting <- filter(sweep_allies_1, 
                                   prop_min %in% interesting_cases)


sweep_allies_1_interesting$prop_min <- paste0(paste0("Minority ", sweep_allies_1_interesting$prop_min*100), "%")

data_lines_1_interesting <- filter(data_lines_1, prop_min %in% interesting_cases)
data_lines_1_interesting$prop_min <- paste0(paste0("Minority ", data_lines_1_interesting$prop_min*100), "%")

# plot
(plot_k_allies_1_interesting <- sweep_allies_1_interesting %>%
    filter(.,  beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion), size = 1.2)+
    facet_wrap(~ as.factor(prop_min))+
    geom_hline(data = data_lines_1_interesting,
             aes(yintercept = hline),
             linetype="dashed")+
    geom_vline(data = data_lines_1_interesting,
               aes(xintercept = vline),
               linetype="dashed")+
        geom_text(data = data_lines_1_interesting, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
            hjust = -0.1, vjust = 1.5) +
    labs(
      title = "Effect of the increase in the % of allies per minority member in top 5% of the nodes ",
      y = "% in top 5% of the nodes",
      x = "Proportion allies",
      x.axis.text=element_text(size=12),
      y.axis.title=element_text(size=14,face="bold")
      ) +
    theme_bw()+
    theme(legend.position = "none",
          strip.text.x = element_text(size = 13),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12)))
    
```



Do the same for the covert minorities:
```{r warning = F, message=F, fig.width=12, fig.height=6}
# data for vertical lines - find proportion of allies for which minorities reach equity
vertical_lines_1 <- sweep_covert_1 %>%
  filter(beta == 0.05)%>%
  dplyr::group_by(beta, prop_covert, prop_min)%>%
  summarise(prop_min_avg = round(mean(prop_min), 2),
            prop_covert_avg = round(mean(prop_covert), 2),
            prop_min_top_k_avg = round(mean(prop_all_minorities_top_k), 2))%>%
  as.data.frame()
  
vertical_lines_1 <- vertical_lines_1[, 4:6]

vertical_lines_1 <- vertical_lines_1 %>%
  group_by(prop_min_avg)%>%
  filter(prop_min_top_k_avg >= (prop_min_avg-0.01))%>%
  slice(which.min(prop_covert_avg))
  
data_lines_1 <- data.frame(prop_min = unique(sweep_covert_1$prop_min),  # Create data for lines
                         hline = unique(sweep_covert_1$prop_min),
                         vline = vertical_lines_1$prop_covert_avg)%>%
  filter(., prop_min < 0.5)

# plot
(plot_k_covert_1 <- sweep_covert_1 %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k) )%>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k))+
    geom_line( color = "red")+
    geom_hline(data = data_lines_1,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_1,
               aes(xintercept = vline),
               linetype="dashed")+
    geom_text(data = data_lines_1, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
            hjust = 0.5, vjust = 1.5) +
    facet_wrap(~ prop_min, ncol = 5,  scales = "free_x")+
    labs(
      title = "Effect of the increase in % of hidden minority on the % of all minorities in top k  - by varying k",
      y = "% of minorities in top-k%",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Proportion minorities", "prop_ally_top_k"="Proportion allies"))+
    theme_bw())
```


Plot some interesting cases:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}

interesting_cases <- c(0.1, 0.2, 0.3, 0.4)


sweep_covert_1_interesting <- filter(sweep_covert_1, 
                                   prop_min %in% interesting_cases)

sweep_covert_1_interesting$prop_min <- paste0(paste0("Minority ", sweep_covert_1_interesting$prop_min*100), "%")

data_lines_1_interesting <- filter(data_lines_1,
                                 prop_min %in% interesting_cases)

data_lines_1_interesting$prop_min <- paste0(paste0("Minority ", data_lines_1_interesting$prop_min*100), "%")


(plot_k_covert_1_diag_interesting <- sweep_covert_1_interesting %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert, prop_covert_rescaled, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k))%>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k))+
    geom_line( color = "red", size = 1)+
    geom_hline(data = data_lines_1_interesting,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_1_interesting,
               aes(xintercept = vline),
               linetype="dashed")+
    geom_text(data = data_lines_1_interesting, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
            hjust = -0.1, vjust = 1.5) +
    facet_wrap(~ prop_min, ncol = 5)+
    labs(
      title = "Effect of the increase in % of the incorporated minority on the % of all minorities in top 5% of the nodes",
      y = "% of minorities in top 5% of nodes",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    theme_bw())

```







## Scenario 2 - more favourable

Read in the files:
```{r message = F, warning = F}
sweep_allies_2 <- read_csv("../..//python/group_A/results dpah4/allies_sweep_per_top_k_setup2.csv")
sweep_allies_2$prop_ally <- round(sweep_allies_2$prop_ally, 2)

sweep_allies_2$prop_ally_min <- sweep_allies_2$prop_ally + sweep_allies_2$prop_min
sweep_allies_2$ally_to_min <- sweep_allies_2$prop_ally / sweep_allies_2$prop_min

sweep_covert_2 <-  read_csv("../..//python/group_A/results dpah4/covert_sweep_per_top_k_setup2.csv")
sweep_covert_2$prop_covert <- round(sweep_covert_2$prop_covert, 2)
```

Plot the share of minorities across different minority share setups, with
the share of minority in top 5% of the nodes:
```{r warning = F, message=F, fig.width=16, fig.height=3.5}

# data for vertical lines - find proportion of allies for which minorities reach equity
vertical_lines_2 <- sweep_allies_2 %>%
  filter(beta == 0.05)%>%
  dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
  summarise(prop_min_avg = round(mean(prop_min), 2),
            prop_ally_avg = round(mean(prop_ally), 2),
            prop_min_top_k_avg = round(mean(prop_min_top_k), 2))%>%
  as.data.frame()
  
vertical_lines_2 <- vertical_lines_2[, 5:7]

vertical_lines_2 <- vertical_lines_2 %>%
  group_by(prop_min_avg)%>%
  filter(prop_min_top_k_avg >= (prop_min_avg - 0.01))%>%
  slice(which.min(prop_ally_avg))
  
data_lines_2 <- data.frame(prop_min = unique(sweep_allies_2$prop_min),  # Create data for lines
                         hline = unique(sweep_allies_2$prop_min),
                         vline = vertical_lines_2$prop_ally_avg)%>%
  filter(., prop_min < 0.5)

# plot
(plot_k_allies_2 <- sweep_allies_2 %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion))+
    facet_wrap(~ prop_min, ncol = 7)+
    geom_hline(data = data_lines_2,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_2,
               aes(xintercept = vline),
               linetype="dashed")+
        geom_text(data = data_lines_2, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
                  hjust = -0.1, vjust = 1)+
    labs(
      title = "Effect of the increase in % of allies on the % of minorities/allies in top k  - by varying minority proportion",
      y = "% of minorities in top-k%",
      x = "Proportion allies",
      color = "Proportion of:") +
    theme_bw())
  
```

Proportion allies to minorities, a few interesting examples:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}
interesting_cases <- c(0.1, 0.2, 0.3)


sweep_allies_2_interesting <- filter(sweep_allies_2, 
                                   prop_min %in% interesting_cases)


sweep_allies_2_interesting$prop_min <- paste0(paste0("Minority ", sweep_allies_2_interesting$prop_min*100), "%")

data_lines_2_interesting <- filter(data_lines_2, prop_min %in% interesting_cases)
data_lines_2_interesting$prop_min <- paste0(paste0("Minority ", data_lines_2_interesting$prop_min*100), "%")

# plot
(plot_k_allies_2_interesting <- sweep_allies_2_interesting %>%
    filter(.,  beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion), size = 1.2)+
    facet_wrap(~ as.factor(prop_min))+
    geom_hline(data = data_lines_2_interesting,
             aes(yintercept = hline),
             linetype="dashed")+
    geom_vline(data = data_lines_2_interesting,
               aes(xintercept = vline),
               linetype="dashed")+
    geom_text(data = data_lines_2_interesting, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
            hjust = -0.1, vjust = 1.5) +
    labs(
      title = "Effect of the increase in the % of allies per minority member in top 5% of the nodes ",
      y = "% in top 5% of the nodes",
      x = "Proportion allies",
      x.axis.text=element_text(size=12),
      y.axis.title=element_text(size=14,face="bold")
      ) +
    theme_bw()+
    theme(legend.position = "none",
          strip.text.x = element_text(size = 13),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12)))
    
```



Do the same for the covert minorities:
```{r warning = F, message=F, fig.width=12, fig.height=6}

# data for vertical lines - find proportion of allies for which minorities reach equity
vertical_lines_2 <- sweep_covert_2 %>%
  filter(beta == 0.05)%>%
  dplyr::group_by(beta, prop_covert, prop_min)%>%
  summarise(prop_min_avg = round(mean(prop_min), 2),
            prop_covert_avg = round(mean(prop_covert), 2),
            prop_min_top_k_avg = round(mean(prop_all_minorities_top_k), 2))%>%
  as.data.frame()
  
vertical_lines_2 <- vertical_lines_2[, 4:6]

vertical_lines_2 <- vertical_lines_2 %>%
  group_by(prop_min_avg)%>%
  filter(prop_min_top_k_avg >= (prop_min_avg-0.01))%>%
  slice(which.min(prop_covert_avg))
  
data_lines_2 <- data.frame(prop_min = unique(sweep_covert_2$prop_min),  # Create data for lines
                         hline = unique(sweep_covert_2$prop_min),
                         vline = vertical_lines_2$prop_covert_avg)%>%
  filter(., prop_min < 0.5)

# plot
(plot_k_covert_2 <- sweep_covert_2 %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k) )%>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k))+
    geom_line( color = "red")+
    geom_hline(data = data_lines_2,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_2,
               aes(xintercept = vline),
               linetype="dashed")+
    facet_wrap(~ prop_min, ncol = 5,  scales = "free_x")+
    labs(
      title = "Effect of the increase in % of hidden minority on the % of all minorities in top k  - by varying k",
      y = "% of minorities in top-k%",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Proportion minorities", "prop_ally_top_k"="Proportion allies"))+
    theme_bw())
```


Plot some interesting cases:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}

interesting_cases <- c(0.1, 0.2, 0.3, 0.4)


sweep_covert_2_interesting <- filter(sweep_covert_2, 
                                   prop_min %in% interesting_cases)

sweep_covert_2_interesting$prop_min <- paste0(paste0("Minority ", sweep_covert_2_interesting$prop_min*100), "%")

data_lines_2_interesting <- filter(data_lines_2,
                                 prop_min %in% interesting_cases)

data_lines_2_interesting$prop_min <- paste0(paste0("Minority ", data_lines_2_interesting$prop_min*100), "%")


(plot_k_covert_2_diag_interesting <- sweep_covert_2_interesting %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert, prop_covert_rescaled, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k))%>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k))+
    geom_line( color = "red", size = 1)+
    geom_hline(data = data_lines_2_interesting,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_2_interesting,
               aes(xintercept = vline),
               linetype="dashed")+
    facet_wrap(~ prop_min, ncol = 5)+
    labs(
      title = "Effect of the increase in % of the incorporated minority on the % of all minorities in top 5% of the nodes",
      y = "% of minorities in top 5% of nodes",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    theme_bw())

```



## Scenario 3 - most favourable

Read in the files:
```{r message = F, warning = F}
sweep_allies_3 <- read_csv("../..//python/group_A/results dpah4/allies_sweep_per_top_k_setup3.csv")
sweep_allies_3$prop_ally <- round(sweep_allies_3$prop_ally, 2)

sweep_allies_3$prop_ally_min <- sweep_allies_3$prop_ally + sweep_allies_3$prop_min
sweep_allies_3$ally_to_min <- sweep_allies_3$prop_ally / sweep_allies_3$prop_min

sweep_covert_3 <-  read_csv("../..//python/group_A/results dpah4/covert_sweep_per_top_k_setup3.csv")
sweep_covert_3$prop_covert <- round(sweep_covert_3$prop_covert, 2)
```

Plot the share of minorities across different minority share setups, with
the share of minority in top 5% of the nodes:
```{r warning = F, message=F, fig.width=16, fig.height=3.5}

# data for vertical lines - find proportion of allies for which minorities reach equity
vertical_lines <- sweep_allies_3 %>%
  filter(beta == 0.05)%>%
  dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
  summarise(prop_min_avg = round(mean(prop_min), 2),
            prop_ally_avg = round(mean(prop_ally), 2),
            prop_min_top_k_avg = round(mean(prop_min_top_k), 2))%>%
  as.data.frame()
  
vertical_lines <- vertical_lines[, 5:7]

vertical_lines <- vertical_lines %>%
  group_by(prop_min_avg)%>%
  filter(prop_min_top_k_avg >= (prop_min_avg - 0.01))%>%
  slice(which.min(prop_ally_avg))
  
data_lines_3 <- data.frame(prop_min = unique(sweep_allies_3$prop_min),  # Create data for lines
                         hline = unique(sweep_allies_3$prop_min),
                         vline = vertical_lines$prop_ally_avg)%>%
  filter(., prop_min < 0.5)

# plot
(plot_k_allies_3 <- sweep_allies_3 %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion))+
    facet_wrap(~ prop_min, ncol = 7)+
    geom_hline(data = data_lines_3,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_3,
               aes(xintercept = vline),
               linetype="dashed")+
        geom_text(data = data_lines_3, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
                  hjust = -0.1, vjust = 1)+
    labs(
      title = "Effect of the increase in % of allies on the % of minorities/allies in top k  - by varying minority proportion",
      y = "% of minorities in top-k%",
      x = "Proportion allies",
      color = "Proportion of:") +
    theme_bw())
  
```

Proportion allies to minorities, a few interesting examples:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}
interesting_cases <- c(0.1, 0.2, 0.3)


sweep_allies_interesting <- filter(sweep_allies, 
                                   prop_min %in% interesting_cases)


sweep_allies_interesting$prop_min <- paste0(paste0("Minority ", sweep_allies_interesting$prop_min*100), "%")

data_lines_interesting <- filter(data_lines_3, prop_min %in% interesting_cases)
data_lines_interesting$prop_min <- paste0(paste0("Minority ", data_lines_interesting$prop_min*100), "%")

# plot
(plot_k_allies_interesting <- sweep_allies_interesting %>%
    filter(.,  beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion), size = 1.2)+
    facet_wrap(~ as.factor(prop_min))+
    geom_hline(data = data_lines_interesting,
             aes(yintercept = hline),
             linetype="dashed")+
    geom_vline(data = data_lines_interesting,
               aes(xintercept = vline),
               linetype="dashed")+
    geom_text(data = data_lines_interesting, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
            hjust = -0.1, vjust = 1.5) +
    labs(
      title = "Effect of the increase in the % of allies per minority member in top 5% of the nodes ",
      y = "% in top 5% of the nodes",
      x = "Proportion allies",
      x.axis.text=element_text(size=12),
      y.axis.title=element_text(size=14,face="bold")
      ) +
    theme_bw()+
    theme(legend.position = "none",
          strip.text.x = element_text(size = 13),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12)))
    
```



Do the same for the covert minorities:
```{r warning = F, message=F, fig.width=12, fig.height=6}
data_hline <- data.frame(prop_min = unique(sweep_covert$prop_min),  # Create data for lines
                         hline = unique(sweep_covert$prop_min))

# data for vertical lines - find proportion of allies for which minorities reach equity
vertical_lines <- sweep_covert_3 %>%
  filter(beta == 0.05)%>%
  dplyr::group_by(beta, prop_covert, prop_min)%>%
  summarise(prop_min_avg = round(mean(prop_min), 2),
            prop_covert_avg = round(mean(prop_covert), 2),
            prop_min_top_k_avg = round(mean(prop_all_minorities_top_k), 2))%>%
  as.data.frame()
  
vertical_lines <- vertical_lines[, 4:6]

vertical_lines <- vertical_lines %>%
  group_by(prop_min_avg)%>%
  filter(prop_min_top_k_avg >= (prop_min_avg-0.01))%>%
  slice(which.min(prop_covert_avg))
  
data_lines_3 <- data.frame(prop_min = unique(sweep_covert$prop_min),  # Create data for lines
                         hline = unique(sweep_covert$prop_min),
                         vline = vertical_lines$prop_covert_avg)%>%
  filter(., prop_min < 0.5)

# plot
(plot_k_covert_3 <- sweep_covert_3 %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k) )%>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k))+
    geom_line( color = "red")+
    geom_hline(data = data_lines_3,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_3,
               aes(xintercept = vline),
               linetype="dashed")+
    facet_wrap(~ prop_min, ncol = 5,  scales = "free_x")+
    labs(
      title = "Effect of the increase in % of hidden minority on the % of all minorities in top k  - by varying k",
      y = "% of minorities in top-k%",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Proportion minorities", "prop_ally_top_k"="Proportion allies"))+
    theme_bw())
```


Plot some interesting cases:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}

interesting_cases <- c(0.1, 0.2, 0.3, 0.4)


sweep_covert_interesting <- filter(sweep_covert, 
                                   prop_min %in% interesting_cases)

sweep_covert_interesting$prop_min <- paste0(paste0("Minority ", sweep_covert_interesting$prop_min*100), "%")

data_lines_interesting <- filter(data_lines,
                                 prop_min %in% interesting_cases)

data_lines_interesting$prop_min <- paste0(paste0("Minority ", data_lines_interesting$prop_min*100), "%")


(plot_k_covert_diag_interesting <- sweep_covert_interesting %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert, prop_covert_rescaled, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k))%>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k))+
    geom_line( color = "red", size = 1)+
    geom_hline(data = data_lines_interesting,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines_interesting,
               aes(xintercept = vline),
               linetype="dashed")+
    facet_wrap(~ prop_min, ncol = 5)+
    labs(
      title = "Effect of the increase in % of the incorporated minority on the % of all minorities in top 5% of the nodes",
      y = "% of minorities in top 5% of nodes",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    theme_bw())

```

## Compare the scenarios?

### Allies 
```{r}
interesting_cases <- c(0.1, 0.2, 0.3)


ally_sweep_1 <- sweep_allies_1 %>%
  filter(., beta == 0.05 & prop_min %in% interesting_cases)%>%
  dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
  dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
  pivot_longer(
  cols = prop_min_top_k,
  names_to = "proportion",
  values_to = "prop")

ally_sweep_1$scenario <- "Scenario 1"

ally_sweep_2 <- sweep_allies_2 %>%
  filter(., beta == 0.05 & prop_min %in% interesting_cases)%>%
  dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
  dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
  pivot_longer(
  cols = prop_min_top_k,
  names_to = "proportion",
  values_to = "prop")

ally_sweep_2$scenario <- "Scenario 2"


ally_sweep_3 <- sweep_allies_3 %>%
  filter(., beta == 0.05 & prop_min %in% interesting_cases)%>%
  dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
  dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
  pivot_longer(
  cols = prop_min_top_k,
  names_to = "proportion",
  values_to = "prop")

ally_sweep_3$scenario <- "Scenario 3"


combined_ally_scenarios <- rbind(ally_sweep_1,
                                 ally_sweep_2,
                                 ally_sweep_3)

data_lines_combined <- data.frame(prop_min = unique(combined_ally_scenarios$prop_min), 
                                  hline = unique(combined_ally_scenarios$prop_min))


combined_ally_scenarios$prop_min <- paste0(paste0("Minority ", combined_ally_scenarios$prop_min*100), "%")
data_lines_combined$prop_min <- paste0(paste0("Minority ", data_lines_combined$prop_min*100), "%")
```

Plot the scenario comparison:
```{r warning = F, fig.width = 10, fig.height = 5}

# plot
(plot_scenarios <- combined_ally_scenarios %>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = scenario), size = 1.2)+
    facet_wrap(~ as.factor(prop_min))+
    geom_hline(data = data_lines_combined,
             aes(yintercept = hline),
             linetype="dashed")+
    labs(
      title = "Effect of the increase in the % of allies per minority member in top 5% of the nodes ",
      y = "% in top 5% of the nodes",
      x = "Proportion allies",
      x.axis.text=element_text(size=12),
      y.axis.title=element_text(size=14,face="bold")
      ) +
    theme_bw()+
    theme(
          strip.text.x = element_text(size = 13),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12)))
    
```





### Integrated minorities 
```{r}
interesting_cases <- c(0.1, 0.2, 0.3, 0.4)


covert_sweep_1 <- sweep_covert_1 %>%
  filter(., beta == 0.05 & prop_min %in% interesting_cases)%>%
  dplyr::group_by(beta, prop_covert, prop_min)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k))

covert_sweep_1$scenario <- "Scenario 1"

covert_sweep_2 <- sweep_covert_2 %>%
  filter(., beta == 0.05 & prop_min %in% interesting_cases)%>%
  dplyr::group_by(beta, prop_covert, prop_min)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k))
                     

covert_sweep_2$scenario <- "Scenario 2"


covert_sweep_3 <- sweep_covert_3 %>%
  filter(., beta == 0.05 & prop_min %in% interesting_cases)%>%
  dplyr::group_by(beta, prop_covert, prop_min)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k))

covert_sweep_3$scenario <- "Scenario 3"


combined_covert_scenarios <- rbind(covert_sweep_1,
                                 covert_sweep_2,
                                 covert_sweep_3)

data_lines_combined <- data.frame(prop_min = unique(combined_covert_scenarios$prop_min), 
                                  hline = unique(combined_covert_scenarios$prop_min))


combined_covert_scenarios$prop_min <- paste0(paste0("Minority ", combined_covert_scenarios$prop_min*100), "%")
data_lines_combined$prop_min <- paste0(paste0("Minority ", data_lines_combined$prop_min*100), "%")
```

Plot the scenario comparison:
```{r warning = F, fig.width = 10, fig.height = 5}

# plot
(plot_scenarios <- combined_covert_scenarios %>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k)) +
    geom_line(aes(color = scenario), size = 1.2)+
    facet_wrap(~ as.factor(prop_min))+
    geom_hline(data = data_lines_combined,
             aes(yintercept = hline),
             linetype="dashed")+
    labs(
      title = "Effect of the increase in the % of covert per minority member in top 5% of the nodes ",
      y = "% in top 5% of the nodes",
      x = "Proportion covert",
      x.axis.text=element_text(size=12),
      y.axis.title=element_text(size=14,face="bold")
      ) +
    theme_bw()+
    theme(
          strip.text.x = element_text(size = 13),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12)))
    
```

