---
title: "R Notebook"
---

Analyzing the top different top 5 percentages in the original setup with
homophily of majorities and minorities of 0.8 towards ingroup and 0.2 towards the 
outgroup. We introduce either a share of majority as allies (majority members
who are treated as the majority by others, but prefer the minority group at the
expense of the majority group); or "invisible" minorities (minority members who
are treated as the majority by the majority and minority groups, but they
act as minority groups themselves).


Three scenarios!


First, load some packages:
```{r message = F, warning = F}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)

```


## Scenario 1 - as before

Read in the files:
```{r message = F, warning = F}
sweep_allies <- read_csv("E:/Projects/Homophily/gui_results/results/extracted_ally_sweep_per_fm_top_k_new.csv")
sweep_allies$prop_ally <- round(sweep_allies$prop_ally, 2)

sweep_allies$prop_ally_min <- sweep_allies$prop_ally + sweep_allies$prop_min
sweep_allies$ally_to_min <- sweep_allies$prop_ally / sweep_allies$prop_min
```

Group into groups:
```{r}
groupings <- findInterval(sort(unique(sweep_allies$prop_min)), seq(0.010, 0.515, 0.015))

groupings_key_1 <- data.frame(group_no = sort(unique(groupings)),
                              group_value = seq(0.010, 0.515, 0.015)[-c(29, 32, 34)])

groupings_key_2 <- data.frame(prop_min = sort(unique(sweep_allies$prop_min)),
                              group_no = groupings)

groupings_key_3 <- merge(groupings_key_1,
                         groupings_key_2,
                         by = "group_no")



sweep_allies_merge <- merge(sweep_allies,
                            groupings_key_3,
                            by = "prop_min")

# average across minority shares and iterations
sweep_allies_grouped <- sweep_allies_merge %>%
  filter(beta == 0.05)%>%
  group_by(group_value, prop_ally)%>%
  summarise(across(everything(), list(mean)))

colnames(sweep_allies_grouped) <- stringr::str_remove(colnames(sweep_allies_grouped), "_1")

sweep_allies_grouped$group_value <- round(sweep_allies_grouped$group_value, 2)
```


Plot the share of minorities across different minority share setups, with
the share of minority in top 5% of the nodes:
```{r warning = F, message=F, fig.width=16, fig.height=3.5}

# data for vertical lines - find proportion of allies for which minorities reach parity
vertical_lines <- sweep_allies_grouped %>%
  filter(beta == 0.05)%>%
  dplyr::group_by(beta, prop_ally_min, group_value, prop_ally)%>%
  summarise(prop_min_avg = round(mean(group_value), 2),
            prop_ally_avg = round(mean(prop_ally), 2),
            prop_min_top_k_avg = round(mean(prop_min_top_k), 2))%>%
  as.data.frame()
  
vertical_lines <- vertical_lines[, 5:7]

vertical_lines <- vertical_lines %>%
  group_by(prop_min_avg)%>%
  filter(prop_min_top_k_avg >= (prop_min_avg))%>%
  slice(which.min(prop_ally_avg))
  
data_lines <- data.frame(prop_min = vertical_lines$prop_min_avg,  # Create data for lines
                         hline = vertical_lines$prop_min_avg,
                         vline = vertical_lines$prop_ally_avg)%>%
  filter(., prop_min < 0.5)

# plot
plot_k_allies <- sweep_allies_grouped %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, group_value, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion))+
    facet_wrap(~ group_value, ncol = 7)+
    geom_hline(data = data_lines,
               aes(yintercept = hline),
               linetype="dashed")+
    geom_vline(data = data_lines,
               aes(xintercept = vline),
               linetype="dashed")+
    labs(
      title = "Effect of the increase in % of allies on the % of minorities/allies in top k  - by varying minority proportion",
      y = "% of minorities in top-k%",
      x = "Proportion allies",
      color = "Proportion of:") +
    theme_bw()

```

Proportion allies to minorities, a few interesting examples:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}

interesting_cases <- c(0.10, 0.20,  0.28)


sweep_allies_interesting <- filter(sweep_allies_grouped, 
                                   round(group_value,3) %in% interesting_cases)


sweep_allies_interesting$prop_min <- paste0(paste0("Minority ", sweep_allies_interesting$group_value*100), "%")

data_lines_interesting <- filter(data_lines, prop_min %in% interesting_cases)
data_lines_interesting$prop_min <- paste0(paste0("Minority ", data_lines_interesting$prop_min*100), "%")

# plot
(plot_k_allies_interesting <- sweep_allies_interesting %>%
    filter(.,  beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_point(aes(color = proportion), size = 1.2)+
    geom_line(aes(color = proportion))+
    facet_wrap(~ as.factor(prop_min))+
    geom_hline(data = data_lines_interesting,
             aes(yintercept = hline),
             linetype="dashed")+
    geom_vline(data = data_lines_interesting,
               aes(xintercept = vline),
               linetype="dashed")+
    geom_text(data = data_lines_interesting, aes(x = vline, label = paste0(vline*100, '% for equity'), y = Inf),
            hjust = -0.1, vjust = 1.5) +
    labs(
      title = "Effect of the increase in the % of allies per minority member in top 5% of the nodes ",
      y = "% in top 5% of the nodes",
      x = "Proportion allies",
      x.axis.text=element_text(size=12),
      y.axis.title=element_text(size=14,face="bold")
      ) +
    theme_bw()+
    theme(legend.position = "none",
          strip.text.x = element_text(size = 13),
          axis.text.x = element_text(size = 10),
          axis.text.y = element_text(size = 10),
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12)))
    
```

