---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

Analyzing the top different top 5 percentages in the original setup with
homophily of majorities and minorities of 0.8 towards ingroup and 0.2 towards the 
outgroup. We introduce either a share of majority as allies (majority members
who are treated as the majority by others, but prefer the minority group at the
expense of the majority group); or "invisible" minorities (minority members who
are treated as the majority by the majority and minority groups, but they
act as minority groups themselves).

First, load some packages:
```{r message = F, warning = F}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)

```

Read in the files:
```{r message = F, warning = F}
sweep_allies <- read_csv("../..//python/group_A/results/ally_sweep_per_fm_top_k.csv")
sweep_allies$prop_ally <- round(sweep_allies$prop_ally, 2)

sweep_allies$prop_ally_min <- sweep_allies$prop_ally + sweep_allies$prop_min
sweep_allies$ally_to_min <- sweep_allies$prop_ally / sweep_allies$prop_min

sweep_covert <-  read_csv("../..//python/group_A/results/covert_sweep_per_fm_top_k.csv")
sweep_covert$prop_covert <- round(sweep_covert$prop_covert, 2)
```

Plot the share of minorities across different minority share setups, with
the share of minority in top 5% of the nodes:
```{r warning = F, message=F, fig.width=16, fig.height=3.5}

data_hline <- data.frame(prop_min = unique(sweep_allies$prop_min),  # Create data for lines
                         hline = unique(sweep_allies$prop_min))%>%
  filter(., prop_min < 0.5)



# plot
(plot_k_allies <- sweep_allies %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k),
                     prop_ally_top_k = mean(prop_ally_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k:prop_ally_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion))+
    facet_wrap(~ prop_min, ncol = 7)+
        geom_hline(data = data_hline,
             aes(yintercept = hline),
             linetype="dashed")+
    labs(
      title = "Effect of the increase in % of allies on the % of minorities/allies in top k  - by varying minority proportion",
      y = "% of minorities in top-k%",
      x = "Proportion allies",
      color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Minorities", "prop_ally_top_k"="Allies"))+
    theme_bw())
  
```

Proportion allies to minorities, a few interesting examples:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}
interesting_cases <- c(0.1, 0.2, 0.3)


sweep_allies_interesting <- filter(sweep_allies, 
                                   prop_min %in% interesting_cases)



sweep_allies_interesting$prop_min <- paste0("prop. minority = ", sweep_allies_interesting$prop_min)


data_hline_interesting <- data.frame(prop_min = unique(sweep_allies_interesting$prop_min),  # Create data for lines
                         hline = interesting_cases)

# plot
(plot_k_allies_interesting <- sweep_allies_interesting %>%
    filter(.,  beta == 0.05)%>%
    dplyr::group_by(beta, prop_ally_min, prop_min, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k),
                     prop_ally_top_k = mean(prop_ally_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k:prop_ally_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=prop_ally, y=prop)) +
    geom_line(aes(color = proportion), size = 1.2)+
    facet_wrap(~ as.factor(prop_min))+
    geom_hline(data = data_hline_interesting,
             aes(yintercept = hline),
             linetype="dashed")+
    labs(
      title = "Effect of the increase in the % of allies per minority member in top 5% of the nodes ",
      y = "% in top 5% of the nodes",
      x = "Proportion allies",
      color = "Proportion of:",
      x.axis.text=element_text(size=12),
      y.axis.title=element_text(size=14,face="bold")
      ) +
    scale_color_hue(labels=c("prop_min_top_k" = "Minorities", "prop_ally_top_k"="Allies"))+
    theme_bw())
  
```

```{r}
png(filename = "Plots/allies_1.png",
    width = 10, height = 3.5, units = "in", res = 600) 

plot_k_allies_interesting

dev.off()
```



Do the same for the covert minorities:
```{r warning = F, message=F, fig.width=12, fig.height=6}
data_hline <- data.frame(prop_min = unique(sweep_covert$prop_min),  # Create data for lines
                         hline = unique(sweep_covert$prop_min))

# %>%
#   filter(., prop_min < 0.4)

# plot
(plot_k_covert <- sweep_covert %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert_rescaled, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k) )%>%
    ggplot(., aes(x=prop_covert_rescaled, y=prop_all_minorities_top_k))+
    geom_line( color = "red")+
    geom_hline(data = data_hline,
               aes(yintercept = hline),
               linetype="dashed")+
    facet_wrap(~ prop_min, ncol = 5,  scales = "free_x")+
    labs(
      title = "Effect of the increase in % of hidden minority on the % of all minorities in top k  - by varying k",
      y = "% of minorities in top-k%",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Proportion minorities", "prop_ally_top_k"="Proportion allies"))+
    theme_bw())
```




With the diagonals:
```{r warning = F, message=F, fig.width=12, fig.height=6}
# plot
(plot_k_covert_diag <- sweep_covert %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert, prop_covert_rescaled, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k) )%>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k))+
    geom_line( color = "red")+
    geom_hline(data = data_hline,
               aes(yintercept = hline),
               linetype="dashed")+
   geom_abline()+
    facet_wrap(~ prop_min, ncol = 5)+
    labs(
      title = "Effect of the increase in % of hidden minority on the % of all minorities in top k  - by varying k",
      y = "% of minorities in top-k%",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Proportion minorities", "prop_ally_top_k"="Proportion allies"))+
    theme_bw())
```

Plot some interesting cases:
```{r warning = F, message=F, fig.width=10, fig.height=3.5}

interesting_cases <- c(0.1, 0.2, 0.3, 0.4)


sweep_covert_interesting <- filter(sweep_covert, 
                                   prop_min %in% interesting_cases)


sweep_covert_interesting$prop_min <- paste0("prop. minority = ", sweep_covert_interesting$prop_min)


data_hline <- data.frame(prop_min = unique(sweep_covert_interesting$prop_min),  # Create data for lines
                         hline = interesting_cases)


(plot_k_covert_diag_interesting <- sweep_covert_interesting %>%
    filter(., beta == 0.05)%>%
    dplyr::group_by(prop_min, prop_covert, prop_covert_rescaled, beta)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k) )%>%
    ggplot(., aes(x=prop_covert, y=prop_all_minorities_top_k))+
    geom_line( color = "red", size = 1)+
    geom_hline(data = data_hline,
               aes(yintercept = hline),
               linetype="dashed")+
   geom_abline()+
    facet_wrap(~ prop_min, ncol = 5)+
    labs(
      title = "Effect of the increase in % of the incorporated minority on the % of all minorities in top 5% of the nodes",
      y = "% of minorities in top 5% of nodes",
      x = "Proportion incorporated minority",
         color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Proportion minorities", "prop_ally_top_k"="Proportion allies"))+
    theme_bw())
```

```{r}
png(filename = "Plots/covert_1.png",
    width = 10, height = 3.5, units = "in", res = 600) 

plot_k_covert_diag_interesting

dev.off()
```


