---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

Analyzing the top different top 5 percentages in the original setup with
homophily of majorities and minorities of 0.8 towards ingroup and 0.2 towards the 
outgroup. We introduce either a share of majority as allies (majority members
who are treated as the majority by others, but prefer the minority group at the
expense of the majority group); or "invisible" minorities (minority members who
are treated as the majority by the majority and minority groups, but they
act as minority groups themselves).

First, load some packages:
```{r message = F, warning = F}
library(readr)
library(tidyr)
library(dplyr)
library(ggplot2)
library()
```

Read in the files:
```{r message = F, warning = F}
sweep_allies <- read_csv("../..//python/group_A/results/ally_sweep_per_top_k_100_reps.csv")
sweep_allies$prop_ally <- round(sweep_allies$prop_ally, 2)


sweep_covert <-  read_csv("../..//python/group_A/results/covert_sweep_per_beta_100_reps.csv")
sweep_covert$prop_covert <- round(sweep_covert$prop_covert, 2)
```

Plot the share of minorities across different values of top k, and across
several ally scenarios:
```{r warning = F, message=F, fig.width=14, fig.height=4}

# extract every third value from our 20 values of ally shares
ally_scenarios <- unique(sweep_allies$prop_ally)[seq(1, length(unique(sweep_allies$prop_ally)), 3)]


# plot
(plot_k_allies <- sweep_allies %>%
    filter(., prop_ally %in% ally_scenarios)%>%
    dplyr::group_by(beta, prop_ally)%>%
    dplyr::summarise(prop_min_top_k = mean(prop_min_top_k),
                     prop_ally_top_k = mean(prop_ally_top_k))%>%
    pivot_longer(
    cols = prop_min_top_k:prop_ally_top_k,
    names_to = "proportion",
    values_to = "prop")%>%
    ggplot(., aes(x=beta, y=prop)) +
    geom_line(aes(color = proportion))+
    geom_hline(yintercept=0.20, linetype="dashed")+
    facet_wrap(~ prop_ally, ncol = 7)+
    labs(
      title = "Effect of the increase in % of allies on the % of minorities/allies in top k  - by varying k",
      y = "% of minorities in top-k%",
      x = "Top k% PageRank",
      color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Proportion minorities", "prop_ally_top_k"="Proportion allies"))+
    theme_bw())
  
```

Do the same for the covert minorities:
```{r warning = F, message=F, fig.width=14, fig.height=4}
# extract every third value from our 20 values of ally shares
covert_scenarios <- unique(sweep_covert$prop_covert)[seq(1, length(unique(sweep_covert$prop_covert)), 3)]


# plot
(plot_k_covert <- sweep_covert %>%
    filter(., prop_covert %in% covert_scenarios)%>%
    dplyr::group_by(beta, prop_covert)%>%
    dplyr::summarise(prop_all_minorities_top_k = mean(prop_all_minorities_top_k) )%>%
    ggplot(., aes(x=beta, y=prop_all_minorities_top_k))+
    geom_line( color = "red")+
    geom_hline(yintercept=0.20, linetype="dashed")+
    facet_wrap(~ prop_covert, ncol = 7)+
    labs(
      title = "Effect of the increase in % of hidden minority on the % of all minorities in top k  - by varying k",
      y = "% of minorities in top-k%",
      x = "Top k% PageRank",
         color = "Proportion of:") +
    scale_color_hue(labels=c("prop_min_top_k" = "Proportion minorities", "prop_ally_top_k"="Proportion allies"))+
    theme_bw())
```

